### 2012-01-14 AffineLieAlgebras/Thesis/3.tex
Equation numbering fixed (no duplicates)

Применяя формулу (\ref{Weyl-Kac22}) к правилам ветвления (\ref{branching13}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu\right) }$ и $\Psi _{\af}^{\left( \nu \right) }$ :
\begin{eqnarray}
\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu
}^{(\mu )}\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:132} \\
\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\af%
}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\af}^{\left( \nu \right) }}{R_{%
\af}}.  \label{singular main}
\end{eqnarray}

В работе \cite{2010arXiv1007.0318L} (см. главу \ref{cha:affine-lie-algebras}) было доказано, что коэффициенты ветвления $b_{\xi }^{\left(\mu\right)}$, отвечающие вложению $\af\hookrightarrow \gf$, удовлетворяют следующим рекуррентным соотношениям:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\af_{\perp }}^{\mu _{\af%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right. \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
}\right) ,
\end{array}
\label{recurrent rel}
\end{equation}
где $\afb$ -- подалгбера, задающаяся корнями  $\gf$, ортогональными ко всем корням $\af$ и $W_{\perp}$ -- подгруппа Вейля, соответствующая $\afb$,
\begin{eqnarray}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
\label{delta a ort}
\end{eqnarray}
\begin{eqnarray}
\widetilde{\af_{\perp }} :=\af_{\perp }\oplus \frak{h}_{\perp }
\qquad \widetilde{\af} :=\af\oplus \frak{h}_{\perp }
\end{eqnarray}
и $\pi$ -- оператор проекции. Если вложение максимально, то оператор проекции становится тривиальным и соотношение (\ref{recurrent rel}) упрощается:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
}+\right. \\
\left. +\sum_{\gamma \in \Gamma _{\af\rightarrow \gf}}s\left(
\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
\end{array}
\label{recurrent relation max}
\end{equation}
Рекурсия задается множеством  $\Gamma _{\af\rightarrow \gf}$, называющимся ``веер вложения''. Оно определяется как носитель $\left\{ \xi \right\} _{\af\rightarrow \gf}$ для коэффициентоной функции $s(\xi )$
\[
\left\{ \xi \right\} _{\af\rightarrow \gf}:=\left\{ \xi \in P_{%
\af}|s(\xi )\neq 0\right\}
\]
возникающей в разложении
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\af}^{+}}\left( 1-e^{
-\alpha }\right) =-\sum_{\gamma \in P_{\af}}s(\gamma )e^{-\gamma };\quad
\label{product}
\end{equation}

@@

Вернемся к соотношению  (\ref{singular main}) и домножим обе стороны на  $R_{\af}$:
\begin{equation}
\frac{1}{\prod_{\beta \in \Delta _{\sfr}^{+}}(1-e^{-\beta })}\Psi _{\gf}^{\left( \mu \right) }=\sum_{\nu \in P_{\af}^{+}}b_{\nu}^{(\mu )}\Psi _{\af}^{\left( \nu \right) }.
\label{singular main-2}
\end{equation}
Здесь первый множитель в левой части -- это формальный элемент, обратный к вееру $\Gamma _{\af\rightarrow \gf}$. Рассмотрим модуль старшего веса $L_{\sfr}^{\nu }$. Вложение $\phi :\Delta _{\sfr\,0}\longrightarrow \Delta_{\gf}$ переводит сингулярный элемент  $\Psi _{\sfr}^{\left( \nu\right) }$ в $\Psi _{\gf}^{\left( \mu \right) }$. Применяя обратный морфизм $\phi ^{-1}$ к произведению $\left( \prod_{\beta \in \Delta_{\sfr}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\sfr}^{\left( \nu \right) }\right) $, мы получаем характер модуля $L_{\sfr}^{\nu }$,

@@

We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}$
and it defines an injection fan $\Gamma _{\frak{a}%
\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.

Since the singular element of $L^{\mu}$ can be
written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
\sum_{w\in W_{\frak{a}}}\epsilon \left( w \right) w\circ \left(
e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho
_{\frak{s}}}\right)$  for branching coefficients we get the
identity \cite{2011arXiv1111.6787L}:
\begin{equation}
  \label{eq:146}
b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}  
\end{equation}
Here the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $, they have the
same Dynkin numbers: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
m_{k}\omega_{(\sfr) k} . \label{new h weight}$ So branching coefficients coincide with weight
multiplicities of $\sfr$-modules.

@@

Now consider the branching of $\gfh$-modules in $\af$-modules and
assume the existence of a splint
$\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
We decompose $\gf$-modules in equation \eqref{eq:149} into
$\af$-modules using property \eqref{eq:146}:
\begin{multline}
  \label{eq:125}
  \mathrm{ch}L^{\hat{\mu}}_{\gfh}=
\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P_{\af}} b^{(\hat{\mu})}_{(\gfh\downarrow\af)\nu}(n) \mathrm{ch} L^{\nu}_{\af}=
\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} b^{(\nu)}_{(\gf\downarrow \af) \xi}\mathrm{ch} L^{\xi}_{\af}=\\
=\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} M^{\widetilde{\nu}}_{  \widetilde{\nu}-\phi^{-1}( \nu-\xi )}\mathrm{ch} L^{\xi}_{\af}
\end{multline}
We see that the similar matrix relation holds for branching
functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
b_{(\gfh\downarrow\gf)}(q)$ and we can write
$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$. So if we know
branching coefficients for the embedding $\gf\subset\gfh$ (for
example, see book \cite{kass1990ala}) we can easily obtain
branching functions for the embedding $\af\subset \gfh$.
\subsection*{Conclusion}
\label{sec:conclusion} We have demonstrated that splint in affine
Lie algebras leads to new relations between theta-functions and
branching functions for branching to finite-dimensional
subalgebras, which can be useful for computations. Further
question is to generalize this analysis to affine subalgebras and
to apply the results to branching in the study of CFT coset
models.

>>>>

Применяя формулу (\ref{Weyl-Kac22}) к правилам ветвления (\ref{branching13}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu\right) }$ и $\Psi _{\af}^{\left( \nu \right) }$ :
\begin{eqnarray}
\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu
}^{(\mu )}\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:171} \\
\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\af%
}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\af}^{\left( \nu \right) }}{R_{%
\af}}.  \label{singular-main}
\end{eqnarray}

В работе \cite{2010arXiv1007.0318L} (см. главу \ref{cha:affine-lie-algebras}) было доказано, что коэффициенты ветвления $b_{\xi }^{\left(\mu\right)}$, отвечающие вложению $\af\hookrightarrow \gf$, удовлетворяют следующим рекуррентным соотношениям:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\af_{\perp }}^{\mu _{\af%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right. \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
}\right) ,
\end{array}
\label{recurrent-rel}
\end{equation}
где $\afb$ -- подалгбера, задающаяся корнями  $\gf$, ортогональными ко всем корням $\af$ и $W_{\perp}$ -- подгруппа Вейля, соответствующая $\afb$,
\begin{eqnarray}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
\label{delta-a-ort}
\end{eqnarray}
\begin{eqnarray}
\widetilde{\af_{\perp }} :=\af_{\perp }\oplus \frak{h}_{\perp }
\qquad \widetilde{\af} :=\af\oplus \frak{h}_{\perp }
\end{eqnarray}
и $\pi$ -- оператор проекции. Если вложение максимально, то оператор проекции становится тривиальным и соотношение (\ref{recurrent-rel}) упрощается:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
}+\right. \\
\left. +\sum_{\gamma \in \Gamma _{\af\rightarrow \gf}}s\left(
\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
\end{array}
\label{recurrent relation max}
\end{equation}
Рекурсия задается множеством  $\Gamma _{\af\rightarrow \gf}$, называющимся ``веер вложения''. Оно определяется как носитель $\left\{ \xi \right\} _{\af\rightarrow \gf}$ для коэффициентоной функции $s(\xi )$
\[
\left\{ \xi \right\} _{\af\rightarrow \gf}:=\left\{ \xi \in P_{%
\af}|s(\xi )\neq 0\right\}
\]
возникающей в разложении
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\af}^{+}}\left( 1-e^{
-\alpha }\right) =-\sum_{\gamma \in P_{\af}}s(\gamma )e^{-\gamma };\quad
\label{product}
\end{equation}

@@

Вернемся к соотношению  (\ref{singular-main}) и домножим обе стороны на  $R_{\af}$:
\begin{equation}
\frac{1}{\prod_{\beta \in \Delta _{\sfr}^{+}}(1-e^{-\beta })}\Psi _{\gf}^{\left( \mu \right) }=\sum_{\nu \in P_{\af}^{+}}b_{\nu}^{(\mu )}\Psi _{\af}^{\left( \nu \right) }.
\label{singular main-2}
\end{equation}
Здесь первый множитель в левой части -- это формальный элемент, обратный к вееру $\Gamma _{\af\rightarrow \gf}$. Рассмотрим модуль старшего веса $L_{\sfr}^{\nu }$. Вложение $\phi :\Delta _{\sfr\,0}\longrightarrow \Delta_{\gf}$ переводит сингулярный элемент  $\Psi _{\sfr}^{\left( \nu\right) }$ в $\Psi _{\gf}^{\left( \mu \right) }$. Применяя обратный морфизм $\phi ^{-1}$ к произведению $\left( \prod_{\beta \in \Delta_{\sfr}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\sfr}^{\left( \nu \right) }\right) $, мы получаем характер модуля $L_{\sfr}^{\nu }$,

@@

We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint-product}$
and it defines an injection fan $\Gamma _{\frak{a}%
\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.

Since the singular element of $L^{\mu}$ can be
written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
\sum_{w\in W_{\frak{a}}}\epsilon \left( w \right) w\circ \left(
e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho
_{\frak{s}}}\right)$  for branching coefficients we get the
identity \cite{2011arXiv1111.6787L}:
\begin{equation}
  \label{eq:146}
b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}  
\end{equation}
Here the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $, they have the
same Dynkin numbers: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
m_{k}\omega_{(\sfr) k} . \label{new-h-weight}$ So branching coefficients coincide with weight
multiplicities of $\sfr$-modules.

@@

Now consider the branching of $\gfh$-modules in $\af$-modules and
assume the existence of a splint
$\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
We decompose $\gf$-modules in equation \eqref{eq:149} into
$\af$-modules using property \eqref{eq:146}:
\begin{multline}
  \label{eq:125}
  \mathrm{ch}L^{\hat{\mu}}_{\gfh}=
\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P_{\af}} b^{(\hat{\mu})}_{(\gfh\downarrow\af)\nu}(n) \mathrm{ch} L^{\nu}_{\af}=
\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} b^{(\nu)}_{(\gf\downarrow \af) \xi}\mathrm{ch} L^{\xi}_{\af}=\\
=\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} M^{\widetilde{\nu}}_{  \widetilde{\nu}-\phi^{-1}( \nu-\xi )}\mathrm{ch} L^{\xi}_{\af}
\end{multline}
We see that the similar matrix relation holds for branching
functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
b_{(\gfh\downarrow\gf)}(q)$ and we can write
$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$. So if we know
branching coefficients for the embedding $\gf\subset\gfh$ (for
example, see book \cite{kass1990ala}) we can easily obtain
branching functions for the embedding $\af\subset \gfh$.
\subsection*{Conclusion}
\label{sec:conclusion-four} We have demonstrated that splint in affine
Lie algebras leads to new relations between theta-functions and
branching functions for branching to finite-dimensional
subalgebras, which can be useful for computations. Further
question is to generalize this analysis to affine subalgebras and
to apply the results to branching in the study of CFT coset
models.

### 2012-01-14 AffineLieAlgebras/Thesis/5.tex
Equation numbering fixed (no duplicates)

Необходимые сведения из теории представлений приведены в главе \ref{cha:affine-lie-algebras}. Здесь мы начинаем с описания структур данных пакета  {\bf Affine.m}, использующихся для описания различных объектов теории представлений  (раздел \ref{sec:core-datastructures}), обсуждаем алгоритмы  (раздел \ref{sec:comp-algor}) и приводим примеры  (раздел \ref{sec:examples}).

@@

\section{Примеры}
\label{sec:examples}
В этом разделе мы приводим примеры вычислений, проведенных с использованием {\bf Affine.m} и код, который для этого потребовался.

>>>>

Необходимые сведения из теории представлений приведены в главе \ref{cha:affine-lie-algebras}. Здесь мы начинаем с описания структур данных пакета  {\bf Affine.m}, использующихся для описания различных объектов теории представлений  (раздел \ref{sec:core-datastructures}), обсуждаем алгоритмы  (раздел \ref{sec:comp-algor}) и приводим примеры  (раздел \ref{sec:examples-six}).

@@

\section{Примеры}
\label{sec:examples-six}
В этом разделе мы приводим примеры вычислений, проведенных с использованием {\bf Affine.m} и код, который для этого потребовался.
